---
title: "assignment_06_KanaparthiVenkata"
author: "Venkata Kanaparthi"
date: "5/13/2021"
output: pdf_document
---

```{r include=TRUE}
library(ggm)
library(ggplot2)
```

Set the working directory to the root of your DSC 520 directory

```{r include=TRUE}
setwd('E:/MSDS-SEM2/DSC520/CodingAssignments/DSC520KANAPARTHI')
## Load the `data/r4ds/heights.csv` to
heights_df <- read.csv("data/r4ds/heights.csv")
```

Fit a linear model using the `age` variable as the predictor and `earn` as the outcome

```{r include=TRUE}
age_lm <- lm(earn ~ age, data = heights_df , na.action = na.exclude)
age_lm
```

View the summary of your model using `summary()`
```{r include=TRUE}
summary(age_lm)
```

Creating predictions using `predict()`

```{r include=TRUE}
age_testing_df <- data.frame(age = c(18,36,54,72,80))
age_predict_df <- data.frame(earn = predict(age_lm, newdata = age_testing_df), age=age_testing_df)
```

## Plot the predictions against the original data
```{r include=TRUE}
ggplot(data = heights_df, aes(y = earn, x = age)) + geom_point(color='blue') +  geom_line(color='red',data = age_predict_df, aes(y=earn, x=age))
```
## Mean on earn
```{r include=TRUE}
mean_earn <- mean(heights_df$earn)
mean_earn
```
## Corrected Sum of Squares Total
```{r include=TRUE}
sst <- sum((mean_earn - heights_df$earn)^2)
sst
```
## Corrected Sum of Squares for Model
```{r include=TRUE}
ssm <- sum((mean_earn - age_predict_df$earn)^2)
ssm
```
## Residuals
```{r include=TRUE}
residuals <- heights_df$earn - age_predict_df$earn
#residuals
```
## Sum of Squares for Error
```{r include=TRUE}
sse <- sum(residuals^2)
sse
```
## R Squared 
```{r include=TRUE}
r_squared <- ssm/sst
r_squared
```
## Number of observations
```{r include=TRUE}
n <- 5
n
```
## Number of regression parameters
```{r include=TRUE}
p <- 2
p
```
## Corrected Degrees of Freedom for Model (p-1)
```{r include=TRUE}
dfm <- p-1
dfm
```
## Degrees of Freedom for Error (n-p)
```{r include=TRUE}
dfe <- n-p
dfe
```
## Corrected Degrees of Freedom Total:   DFT = n - 1
```{r include=TRUE}
dft <- n-1
dft
```
## Mean of Squares for Model:   MSM = SSM / DFM
```{r include=TRUE}
msm <- ssm/dfm
msm
```
## Mean of Squares for Error:   MSE = SSE / DFE
```{r include=TRUE}
mse <- sse/dfe
mse
```
## Mean of Squares Total:   MST = SST / DFT
```{r include=TRUE}
mst <- sst/dft
mst
```
## F Statistic F = MSM/MSE
```{r include=TRUE}
f_score <- msm/mse
f_score
```
## Adjusted R Squared R2 = 1 - (1 - R2)(n - 1) / (n - p)
```{r include=TRUE}
adjusted_r_squared <- 1-((1 - r_squared)*(n - 1) / (n - p))
adjusted_r_squared
```
## Calculate the p-value from the F distribution
```{r include=TRUE}
p_value <- pf(f_score, dfm, dft, lower.tail=F)
p_value
```